Naturalness in U(1) extensions of the MSSM

### 2014-12-18 paper/e6ssm-tuning-paper.tex
Removed italicised text, removed reference to 2-loop corrections to the effective potential - could be confusing if not distinguished between 2-loop RGE effects and the 2-loop effective potential

Written in the form of Eq. (\ref{eq:E6MZequation}) we see the potential new source of fine tuning alluded to above, in the form of the third term on the right-hand side. For large values of the VEV $s$, the $D$-term contributions can be quite a bit larger than $M_Z^2$. In particular, recent experimental limits \cite{Aad:2014cka} require that the $Z'$ mass be large, with bounds of $M_{Z'}\gtrsim 2.51$ TeV in $U(1)_\psi$ models and $M_{Z'}\gtrsim 2.62$ TeV in $U(1)_\chi$ models. To satisfy these limits typically requires large values of the singlet VEV $s$. For example $s\gtrsim 6$ TeV is required in the E$_6$SSM with $U(1)'=U(1)_N$, so that $|D_{H_1}|,|D_{H_2}|\gg M_Z^2$ for $E_6$ models with $\tilde{Q}_S\neq 0$. As a result the remaining terms on the right-hand side of Eq. (\ref{eq:E6MZequation}) must be tuned to cancel the resulting very large contribution to $M_Z$. Moreover, because this is a large \textit{tree level} fine tuning, it may negate the increase in naturalness that is associated with having a reduced need for heavy superpartners. In $U(1)$ extended models for which $\tilde{Q}_S\neq 0$, the importance of the $Z^\prime$ mass to the fine tuning in these models can be made even clearer by writing Eq. (\ref{eq:E6MZequation}) in the form given in \cite{Athron:2013ipa},

@@

However, it is well known in the MSSM that radiative corrections can significantly change (indeed, reduce) the fine tuning \cite{Cassel:2010px}. It is therefore important when studying the fine tuning to include one- and two-loop corrections to the effective potential in the fine tuning measure. To do so it is most convenient to work in terms of the EWSB conditions Eq. (\ref{eq:E6EWSBConditions}), rather than Eq. (\ref{eq:E6MZequation}). The general procedure is as follows \cite{Ellwanger:2011mu}. For a model in which $m$ fields develop real VEVs (e.g. $m=2$ in the MSSM, $m=3$ in the NMSSM and in the $E_6$ models considered), we require that the $m$ minimization conditions

>>>>

Written in the form of Eq. (\ref{eq:E6MZequation}) we see the potential new source of fine tuning alluded to above, in the form of the third term on the right-hand side. For large values of the VEV $s$, the $D$-term contributions can be quite a bit larger than $M_Z^2$. In particular, recent experimental limits \cite{Aad:2014cka} require that the $Z'$ mass be large, with bounds of $M_{Z'}\gtrsim 2.51$ TeV in $U(1)_\psi$ models and $M_{Z'}\gtrsim 2.62$ TeV in $U(1)_\chi$ models. To satisfy these limits typically requires large values of the singlet VEV $s$. For example $s\gtrsim 6$ TeV is required in the E$_6$SSM with $U(1)'=U(1)_N$, so that $|D_{H_1}|,|D_{H_2}|\gg M_Z^2$ for $E_6$ models with $\tilde{Q}_S\neq 0$. As a result the remaining terms on the right-hand side of Eq. (\ref{eq:E6MZequation}) must be tuned to cancel the resulting very large contribution to $M_Z$. Moreover, because this is a large tree level fine tuning, it may negate the increase in naturalness that is associated with having a reduced need for heavy superpartners. In $U(1)$ extended models for which $\tilde{Q}_S\neq 0$, the importance of the $Z^\prime$ mass to the fine tuning in these models can be made even clearer by writing Eq. (\ref{eq:E6MZequation}) in the form given in \cite{Athron:2013ipa},

@@

However, it is well known in the MSSM that radiative corrections can significantly change (indeed, reduce) the fine tuning \cite{Cassel:2010px}. It is therefore important when studying the fine tuning to include loop corrections to the effective potential in the fine tuning measure. To do so it is most convenient to work in terms of the EWSB conditions Eq. (\ref{eq:E6EWSBConditions}), rather than Eq. (\ref{eq:E6MZequation}). The general procedure is as follows \cite{Ellwanger:2011mu}. For a model in which $m$ fields develop real VEVs (e.g. $m=2$ in the MSSM, $m=3$ in the NMSSM and in the $E_6$ models considered), we require that the $m$ minimization conditions
